Supplementary Materials

### 2020-07-30 Writeup/manuscript.tex
updated figures
adjusting figure margins and dimensions

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../figures/figure1.png}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/subgroup_comprms_Occ_Odd.png}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{../figures/figure1.png}
\caption{Examplar stimulus for each of the 16 wallpaper groups, with corresponding <something EEG> and a boxplot showing the distribution of display duration thresholds. }
\label{fig:durations_rotations}
\end{figure}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/subgroup_comp_eeg_rms.pdf}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/subgroup_comp_psychophysical.pdf}
\caption{Posterior distributions for the difference in mean display duration threshold. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/model_roc_style.pdf}
\caption{Posterior distributions for the difference in mean RMS EEG response. Colour coding of the text indicates the index of the subgroup, while the colour of the filled distribution relates to the conditional probability that the difference in means is greater than zero. We can see that 55/64 subgroup relationships have $p(\Delta|data)>0.9$.}
\label{fig:durations_rotations}
\end{figure}

### 2020-07-30 analysis/analysis.Rmd
adjusting figure margins and dimensions

```{r, fig.height=8, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero.", cache=TRUE}

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts

@@

```{r ,fig.height=8, cache = TRUE, fig.cap="Distributions of the difference in mean log display duration threshold between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being less than zero."}

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
```

@@

```{r fig.height=8, cache=TRUE, echo = FALSE, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero."}

>>>>

```{r, fig.height=8, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero."}

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_eeg_rms.pdf", width = 6, height = 9)
```

@@

```{r ,fig.height=8, fig.cap="Distributions of the difference in mean log display duration threshold between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being less than zero."}

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_psychophysical.pdf", width = 6, height = 6)
```

@@

```{r fig.height=8, echo = FALSE, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero."}
